Using traffic analysis to identify The Second Generation Onion Router

### 2011-05-15 thesis/experiment.tex
Detailed netAI software

>>>>

  \item netAI Software

  netAI is capable of processing packet traces such as the one produced by
  tcpdump, analysing flows and producing ARFF files containing every flow
  identified as an individual instance \parencite{swinbut:2006fk}. Each instance
  includes many attributes produced from statistical analysis of these flows
  which are useful for traffic classification. An explanation of the statistics
  gathered by netAI is included in table \ref{table:netmate-attributes}.
